Calendar-based graphics for visualising people's daily schedules

### 2017-07-10 main.Rmd
Restructure a bit after meeting with Di

---
author:
  - name: Earo Wang
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{earo.wang@monash.edu}
  - name: Dianne Cook
    affiliation: Monash Univeristy
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{dicook@monash.edu}
  - name: Rob J Hyndman
    affiliation: Monash Univeristy
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{rob.hyndman@monash.edu}
title:
  formatted: "Calendar-based graphics for visualising people's daily schedules"
  plain: "Calendar-based graphics for visualising people's daily schedules"
abstract: >
  It is challenging to visualise people's daily schedules as such data are often of multiple seasons and of long time span. One example is Melbourne pedestrian sensor data which are collected at hourly interval and at a number of locations. Owing to human activities, the data features multiple temopral scales such as time of day, day of week, day of year. We develop the \code{frame\_calendar} function that provides a method for rearranging such kind of data in a calendar-based format and accomplishing visualisation with the grammar of graphics, and describe its construction in detail. We provide some examples to demonstrate its usage by applying to the pedetrian data.
keywords:
  # at least one keyword must be supplied
  formatted: [calendar-based visualisation, temporal-context data]
  plain:     [calendar-based visualisation, temporal-context data]
preamble: >
  \usepackage{amsmath}
output: 
  rticles::jss_article:
  citation_package: biblatex
bibliography: ["references.bib", "packages.bib"]
---

@@

```{r time-series-plot, fig.height = 10.5, fig.cap = "Time series plot about the number of pedestrians over the year of 2016 at a selection of 7 sensors in the city of Melbourne. Coloured by the sensors, small multiples of lines show that the foot traffic varies from one sensor to another in terms of both time and number. The traffic, specifically at two train stations (Flagstaff Station and Flinders Street Station), is primarily driven by the commuters, as depicted in the graph."}
```

```{r facet-time, fig.height = 10.5, fig.cap = "Hourly pedestrian counts facetted by sensors and days of the week using lines. It features at least two types of seasons--time of day and day of week--across all the sensors. The temporal patterns are subject to the sensor locations too."}
```

@@

## Grid construction
\label{sec:grid}

@@

@@

Section \ref{sec:grid} discusses the implementation applied to the fixed scale which is using the whole range of all the data values. The \code{scale} argument controls the scaling of the display. In addition to the fixed scale (\code{fixed}), the remaining options include free scale on all the days (\code{free}), day of the week only (\code{free_wday}), and day of the month only (\code{free_mday}) for different comparisons.

@@

@@

# Examples
\label{sec:examples}

## Lag scatterplot

## Overlaying graph

@@

## Boxplot

@@

```{r write-bib}
write_bib(c( .packages()), 'packages.bib')
```

>>>>

---
author:
  - name: Earo Wang
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{earo.wang@monash.edu}
  - name: Dianne Cook
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{dicook@monash.edu}
  - name: Rob J Hyndman
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{rob.hyndman@monash.edu}
title:
  formatted: "Calendar-based graphics for visualising people's daily schedules"
  plain: "Calendar-based graphics for visualising people's daily schedules"
abstract: >
  It is challenging to visualise people's daily schedules as such data are often of multiple seasons and of long time span. One example is Melbourne pedestrian sensor data which are collected at hourly interval and at a number of locations. Owing to human activities, the data features multiple temporal scales such as time of day, day of week, day of year. We develop the \code{frame\_calendar} function that provides a method for rearranging such kind of data in a calendar-based format and accomplishing visualisation with the grammar of graphics, and describe its construction in detail. We provide some examples to demonstrate its usage by applying to the pedetrian data.
keywords:
  # at least one keyword must be supplied
  formatted: [calendar-based visualisation, temporal-context data]
  plain:     [calendar-based visualisation, temporal-context data]
preamble: >
  \usepackage{amsmath}
output: 
  rticles::jss_article:
  citation_package: biblatex
bibliography: ["references.bib", "packages.bib"]
---

@@

```{r time-series-plot, fig.height = 6, fig.cap = "Time series plot about the number of pedestrians over the year of 2016 at a selection of 7 sensors in the city of Melbourne. Coloured by the sensors, small multiples of lines show that the foot traffic varies from one sensor to another in terms of both time and number. The traffic, specifically at two train stations (Flagstaff Station and Flinders Street Station), is primarily driven by the commuters, as depicted in the graph."}
```

```{r facet-time, fig.height = 6, fig.cap = "Hourly pedestrian counts facetted by sensors and days of the week using lines. It features at least two types of seasons--time of day and day of week--across all the sensors. The temporal patterns are subject to the sensor locations too."}
```

@@

@@

# Options

## Layouts

@@

Section \ref{sec:algorithm} discusses the implementation applied to the fixed scale which is using the whole range of all the data values. The \code{scale} argument controls the scaling of the display. In addition to the fixed scale (\code{fixed}), the remaining options include free scale on all the days (\code{free}), day of the week only (\code{free_wday}), and day of the month only (\code{free_mday}) for different comparisons.

@@

## Polar coordinates

@@

# Variations
\label{sec:examples}

## Overlaying subsets

@@

## Different types of plots

@@

```{r write-bib}
write_bib(c(.packages()), 'packages.bib')
```

### 2017-07-10 main.tex
Restructure a bit after meeting with Di

\author{
Earo Wang\\Monash University \And Dianne Cook\\Monash Univeristy \And Rob J Hyndman\\Monash Univeristy
}
\title{Calendar-based graphics for visualising people's daily schedules}

@@

\Abstract{
It is challenging to visualise people's daily schedules as such data are
often of multiple seasons and of long time span. One example is
Melbourne pedestrian sensor data which are collected at hourly interval
and at a number of locations. Owing to human activities, the data
features multiple temopral scales such as time of day, day of week, day
of year. We develop the \code{frame\_calendar} function that provides a
method for rearranging such kind of data in a calendar-based format and
accomplishing visualisation with the grammar of graphics, and describe
its construction in detail. We provide some examples to demonstrate its
usage by applying to the pedetrian data.
}

@@

      Dianne Cook\\
  Monash Univeristy\\
  Department of Econometrics and Business Statistics, Monash University,
  VIC 3800 Australia\\
  E-mail: \email{dicook@monash.edu}\\

      Rob J Hyndman\\
  Monash Univeristy\\
  Department of Econometrics and Business Statistics, Monash University,
  VIC 3800 Australia\\
  E-mail: \email{rob.hyndman@monash.edu}\\

@@

\subsection{Grid construction}\label{grid-construction}

\label{sec:grid}

@@

@@

@@

\section{Examples}\label{examples}

@@

\subsection{Overlaying graph}\label{overlaying-graph}

>>>>

\author{
Earo Wang\\Monash University \And Dianne Cook\\Monash University \And Rob J Hyndman\\Monash University
}
\title{Calendar-based graphics for visualising people's daily schedules}

@@

\Abstract{
It is challenging to visualise people's daily schedules as such data are
often of multiple seasons and of long time span. One example is
Melbourne pedestrian sensor data which are collected at hourly interval
and at a number of locations. Owing to human activities, the data
features multiple temporal scales such as time of day, day of week, day
of year. We develop the \code{frame\_calendar} function that provides a
method for rearranging such kind of data in a calendar-based format and
accomplishing visualisation with the grammar of graphics, and describe
its construction in detail. We provide some examples to demonstrate its
usage by applying to the pedetrian data.
}

@@

      Dianne Cook\\
  Monash University\\
  Department of Econometrics and Business Statistics, Monash University,
  VIC 3800 Australia\\
  E-mail: \email{dicook@monash.edu}\\

      Rob J Hyndman\\
  Monash University\\
  Department of Econometrics and Business Statistics, Monash University,
  VIC 3800 Australia\\
  E-mail: \email{rob.hyndman@monash.edu}\\

@@

@@

\section{Options}\label{options}

\subsection{Layouts}\label{layouts}

@@

\subsection{Polar coordinates}\label{polar-coordinates}

@@

\section{Other variations}\label{other-variations}

@@

\subsection{Overlaying subsets}\label{overlaying-subsets}
